\bf Title here

### 2020-09-10 paper/paper.Rmd
a recent update on simulation based on recent development of tourr pacakge, polish related data is pending.

```{r kol-cdf,fig.asp=0.5, fig.cap = "\\label{kol-cdf}Comparison of two different searching methods: search_geodesic and search_better on 1D projection problem for a noisier index: kol_cdf. The geodesic search rely heavily on the polishing step to find the final index value while search better works well."}
p1 <- bind_rows(kol_cdf_1d_geodesic, kol_cdf_1d_geodesic_polish) %>% explore_trace_interp(col = method)  + ggtitle("search_geodesic")

p2 <- bind_rows(kol_cdf_1d_better, kol_cdf_1d_better_polish) %>% explore_trace_interp(col = method) + ggtitle("search_better")

@@

```{r 1d-2var-different-seeds,  fig.asp=0.5, fig.cap="\\label{1d-2var-different-seeds}The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum."}
colour <- ferrn::botanical_pal()(3)
p5 <- kol_cdf_1d_2var_better %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[2]) + ggtitle("search_better, seed 123456")
p6 <- kol_cdf_1d_2var_better_2 %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[1]) + ggtitle("search_better, seed 12345")

@@

```{r 1d-2var-better-random, fig.asp=0.5, fig.cap = "\\label{1d-2var-better-random}Using search better random for the problem above will result in finding the global maximum but much larger number of iteration is needed."}
kol_cdf_1d_2var_better_random %>% 
  explore_trace_interp(col = 0) + 
  ylim(0, 0.25) + 
  scale_colour_manual(values = colour[3]) + 
  theme(legend.position = "none") + 
  ggtitle("search_better_random")
```

>>>>

```{r kol-cdf,fig.asp=0.5, fig.cap = "\\label{kol-cdf}Comparison of two different searching methods: search_geodesic and search_better on 1D projection problem for a noisier index: kol_cdf. The geodesic search rely heavily on the polishing step to find the final index value while search better works well."}
# p1 <- bind_rows(kol_1d_geo, kol_1d_geodesic_polish) %>% explore_trace_interp(col = method)  + ggtitle("search_geodesic")
# 
# p2 <- bind_rows(kol_1d_better, kol_1d_better_polish) %>% explore_trace_interp(col = method) + ggtitle("search_better")
# 
# (p1 | p2 ) & theme(legend.position = "bottom") & ylim(0, 0.23)

p1 <- kol_1d_geo %>% explore_trace_interp(col = method)  + ggtitle("search_geodesic")

p2 <- kol_1d_better %>% explore_trace_interp(col = method) + ggtitle("search_better")

@@

```{r 1d-2var-different-seeds,  fig.asp=0.5, fig.cap="\\label{1d-2var-different-seeds}The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum."}
colour <- ferrn::botanical_pal()(3)
p5 <- kol_1d_2var_better %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[2]) + ggtitle("search_better, seed 123456")
p6 <- kol_1d_2var_better_2 %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[1]) + ggtitle("search_better, seed 12345")

@@

```{r 1d-2var-better-random, fig.asp=0.5, fig.cap = "\\label{1d-2var-better-random}Using search better random for the problem above will result in finding the global maximum but much larger number of iteration is needed."}
kol_1d_2var_better_random %>% 
  explore_trace_interp(col = 0) + 
  ylim(0, 0.25) + 
  scale_colour_manual(values = colour[3]) + 
  theme(legend.position = "none") + 
  ggtitle("search_better_random")
```

### 2020-09-10 paper/paper.tex
figured out a way to display the animation using 16 frames - bad plot for now
a recent update on simulation based on recent development of tourr pacakge, polish related data is pending.

@@

@@

\begin{verbatim}
## # A tibble: 10 x 8
##       id basis             index_val info         tries  loop method       alpha
##    <int> <list>                <dbl> <chr>        <dbl> <dbl> <chr>        <dbl>
##  1     1 <dbl[,1] [5 x 1]>     0.749 new_basis        1     1 <NA>           0.5
##  2     2 <dbl[,1] [5 x 1]>     0.730 random_sear~     2     1 search_bett~   0.5
##  3     3 <dbl[,1] [5 x 1]>     0.743 random_sear~     2     2 search_bett~   0.5
##  4     4 <dbl[,1] [5 x 1]>     0.736 random_sear~     2     3 search_bett~   0.5
##  5     5 <dbl[,1] [5 x 1]>     0.747 random_sear~     2     4 search_bett~   0.5
##  6     6 <dbl[,1] [5 x 1]>     0.725 random_sear~     2     5 search_bett~   0.5
##  7     7 <dbl[,1] [5 x 1]>     0.752 new_basis        2     6 search_bett~   0.5
##  8     8 <dbl[,1] [5 x 1]>     0.749 interpolati~     2     0 search_bett~  NA  
##  9     9 <dbl[,1] [5 x 1]>     0.750 interpolati~     2     1 search_bett~  NA  
## 10    10 <dbl[,1] [5 x 1]>     0.750 interpolati~     2     2 search_bett~  NA
\end{verbatim}

>>>>

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/animated-pca-1.pdf}
\caption{\label{animated-pca} 16 frames from animated PCA plot .}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  how does the printed data object looks like?
\end{enumerate}

Do I talk about the work done in the tourr package?

@@

\begin{verbatim}
## # A tibble: 10 x 8
##       id basis             index_val info         tries  loop method       alpha
##    <int> <list>                <dbl> <chr>        <dbl> <dbl> <chr>        <dbl>
##  1     1 <dbl[,1] [5 x 1]>     0.749 new_basis        1     1 <NA>           0.5
##  2     2 <dbl[,1] [5 x 1]>     0.730 random_sear~     2     1 search_bett~   0.5
##  3     3 <dbl[,1] [5 x 1]>     0.743 random_sear~     2     2 search_bett~   0.5
##  4     4 <dbl[,1] [5 x 1]>     0.736 random_sear~     2     3 search_bett~   0.5
##  5     5 <dbl[,1] [5 x 1]>     0.747 random_sear~     2     4 search_bett~   0.5
##  6     6 <dbl[,1] [5 x 1]>     0.725 random_sear~     2     5 search_bett~   0.5
##  7     7 <dbl[,1] [5 x 1]>     0.752 new_basis        2     6 search_bett~   0.5
##  8     8 <dbl[,1] [5 x 1]>     0.749 interpolati~     2     1 search_bett~  NA  
##  9     9 <dbl[,1] [5 x 1]>     0.750 interpolati~     2     2 search_bett~  NA  
## 10    10 <dbl[,1] [5 x 1]>     0.750 interpolati~     2     3 search_bett~  NA
\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\item
\end{enumerate}
